\documentclass[11pt]{amsart}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage{xcolor}
\definecolor{darkblue}{RGB}{0,0,139}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% Notation
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\abs}[1]{\lvert #1 \rvert}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\ip}[2]{\langle #1,#2\rangle}
\newcommand{\eps}{\varepsilon}
\newcommand{\sign}{\operatorname{sign}}
\newcommand{\card}[1]{\lvert #1 \rvert}
\newcommand{\tail}{\operatorname{tail}}
\newcommand{\restr}{\operatorname{head}}
\newcommand{\Span}{\operatorname{span}}
\newcommand{\supp}{\operatorname{supp}}
\DeclareMathOperator{\concFn}{Q}
\DeclareMathOperator{\smallBall}{\rho}

% Lean cross-references (breakable at _ and .; always upright mono)
\newcommand{\lnbrk}{\penalty100\hskip0pt plus 1pt\relax}
\newcommand{\leanfont}{\normalfont\ttfamily\color{darkblue}}
% block-level lean name (after a theorem statement)
\newcommand{\leanname}[1]{%
  \par\noindent\begingroup\footnotesize\leanfont
  \def\_{\char`\_\lnbrk}\def\.{\char`\.\lnbrk}%
  #1\endgroup\par\smallskip}
\newcommand{\privateleanname}[1]{%
  \par\noindent\begingroup\footnotesize\leanfont
  \def\_{\char`\_\lnbrk}\def\.{\char`\.\lnbrk}%
  #1\endgroup\par\smallskip}
% inline lean name (within running text)
\newcommand{\leanref}[1]{%
  {\footnotesize\leanfont
  \def\_{\char`\_\lnbrk}\def\.{\char`\.\lnbrk}%
  #1}}

\title{A Quantitative Proof of Stable Phase Retrieval}
\author{Pedro Abdalla Teixeira\textsuperscript{1}}
\author{Jaume de Dios Pont\textsuperscript{2}}
\author{Jo\~ao Pedro Ramos\textsuperscript{3}}
\author{Mitchell Taylor\textsuperscript{4}}

\begin{document}
\begin{abstract}
We give a fully explicit stability bound for phase retrieval in spans of
independent real-valued random variables under a uniform two-sided $L^1$
bound. If $\xi_1,\dots,\xi_n$ are independent, centered, unit-variance random
variables satisfying $A \le \E[\abs{\xi_i}] \le B$ for fixed $0 < A \le B < 1$,
then for any orthogonal unit vectors $a,b \in \R^n$ the modulus gap
$\sqrt{\E[(\abs{X_a}-\abs{X_b})^2]}$ is at least $c_\perp(A,B) > 0$, where
$c_\perp$ depends only on $A$ and $B$.

This result is the quantitative counterpart of the compactness proof of
stable phase retrieval \cite{compactness}. Each step of the compactness
argument---bounded probes, profile decomposition, head identification,
tail rigidity---is replaced by an explicit finite-dimensional estimate
with computable constants. The entire proof has been formalized in Lean~4
using the Mathlib library; Lean theorem names are recorded throughout.
\end{abstract}
\maketitle
\begingroup
\renewcommand{\thefootnote}{\arabic{footnote}}
\footnotetext[1]{Department of Mathematics, University of California, Irvine, Irvine, California 92697, USA}
\footnotetext[2]{Center for Data Science, New York University, New York, New York 10011, USA}
\footnotetext[3]{Instituto de Matem\'atica Pura e Aplicada (IMPA), Rio de Janeiro, RJ, Brazil}
\footnotetext[4]{Department of Mathematics, ETH Z\"urich, Z\"urich, Switzerland}
\endgroup

\input{Introduction}
\input{Dichotomy}
\input{AuxiliaryEstimates}
\input{HeadIdentification}
\input{DiffuseBranch}

\appendix
\input{Appendix}

\begin{thebibliography}{10}

\bibitem{alaifari2017continuous}
R.~Alaifari and P.~Grohs.
\newblock Phase retrieval in the general setting of continuous frames for
  {B}anach spaces.
\newblock \emph{SIAM J.\ Math.\ Anal.}, 49(3):1895--1911, 2017.

\bibitem{alaifari2021gabor}
R.~Alaifari and P.~Grohs.
\newblock Gabor phase retrieval is severely ill-posed.
\newblock \emph{Appl.\ Comput.\ Harmon.\ Anal.}, 50:401--419, 2021.

\bibitem{compactness}
P.~Abdalla~Teixeira, J.~de~Dios~Pont, J.~P.~Ramos, and M.~Taylor.
\newblock A compactness proof of stable phase retrieval.
\newblock Preprint, 2025.

\bibitem{bandeira2014saving}
A.~S.~Bandeira, J.~Cahill, D.~G.~Mixon, and A.~A.~Nelson.
\newblock Saving phase: injectivity and stability for phase retrieval.
\newblock \emph{Appl.\ Comput.\ Harmon.\ Anal.}, 37(1):106--125, 2014.

\bibitem{cahill2016infinite}
J.~Cahill, P.~G.~Casazza, and I.~Daubechies.
\newblock Phase retrieval in infinite-dimensional {H}ilbert spaces.
\newblock \emph{Trans.\ Amer.\ Math.\ Soc.\ Ser.~B}, 3:63--76, 2016.

\bibitem{calderbank2022stable}
R.~Calderbank, I.~Daubechies, D.~Freeman, and N.~Freeman.
\newblock Stable phase retrieval for infinite dimensional subspaces of
  $L_2(\mathbb{R})$.
\newblock arXiv:2203.03135, 2022.

\bibitem{christ2022examples}
M.~Christ, B.~Pineau, and M.~A.~Taylor.
\newblock Examples of {H}\"older-stable phase retrieval.
\newblock \emph{Math.\ Res.\ Lett.}, 31(5):1339--1352, 2024.

\bibitem{eldar2014stability}
Y.~C.~Eldar and S.~Mendelson.
\newblock Phase retrieval: stability and recovery guarantees.
\newblock \emph{Appl.\ Comput.\ Harmon.\ Anal.}, 36(3):473--494, 2014.

\bibitem{FOTP}
D.~Freeman, T.~Oikhberg, B.~Pineau, and M.~A.~Taylor.
\newblock Stable phase retrieval in function spaces.
\newblock \emph{Math.\ Ann.}, 390(1):1--43, 2024.

\bibitem{grohs2020survey}
P.~Grohs, S.~Koppensteiner, and M.~Rathmair.
\newblock Phase retrieval: uniqueness and stability.
\newblock \emph{SIAM Rev.}, 62(2):301--350, 2020.

\end{thebibliography}

\end{document}
